\documentclass[a4paper]{article}

\usepackage[official]{eurosym}
\usepackage{babel}
\usepackage{hyperref}

\title{Procès-verbal de l'assemblée générale 2022}
\date{7 septembre 2022}

\begin{document}

\maketitle

L'assemblée générale ordinaire du Comité pour l'Accessibilité aux Publications
en Sciences et Humanités (C.A.P.S.H.) s'est tenue le 9 septembre 2022 à 19h30,
sur la plateforme de discussion en ligne Zoom.

\begin{itemize}
  \item Présidence de séance : Antoine Amarilli
  \item Secrétaire de séance : Antoine Amarilli
  \item Liste des présents : Antoine Amarilli, Antonin Delpeuch, Marie Farge, Pierre Senellart
\end{itemize}

\section{Ordre du jour}

\begin{itemize}
\item Bilan moral
\item Bilan financier
\item Élection du conseil d'administration
\item Disccussions diverses
\end{itemize}

\section{Bilan moral}

Pierre Senellart présente le bilan moral de l'association (en anglais).

There were some bugfixes to the platform, in particular fixing the Shibboleth authentication. Work is underway to import new data sources: Sherpa/RoMEO, Crossref. It is planned to import the new BASE dump. The TU Darmstadt library is still interested and we had discussions with them, the next such meeting is planned in a few weeks, also including Braunschweig who are still having authentication issues, possibly linked to differences in the exact format of the data that the identity provider is providing. There are other related issues, e.g., with non-ASCII characters.

The plan is to finish these two tasks, and then move on to more ambitious tasks.

We will request an extension of the project to cover the end of N's contract and have some time to finish things up afterwards. We can request an extension of the project by 6 months.

Le bilan moral est mis aux voix et il est approuvé à l'unanimité.

\section{Bilan financier}

Antoine Amarilli présente le bilan financier de l'association (en anglais).

At the latest financial report at the 2021 AGM on August 20, 2021, our bank account contained 1790.77 EUR.

Since then the following happened:

Spendings (total 1845.26 EUR):
\begin{itemize}
  \item Online hosting: 1751.96 EUR
    \begin{itemize}
      \item 145.15 EUR 4 times
      \item 149.95 EUR 6 times
      \item 150.23 EUR 2 times (went via Antoine Amarilli because of payment incident, includes Wise fees)
    \end{itemize}
      \item Domain name reimbursement (Antoine Amarilli) : 64.50 EUR
\end{itemize}

Income (total 884.56 EUR):
\begin{itemize}
  \item ENS 870.90 EUR to pay for 6 months of server hosting
  \item Donations on Liberapay:
    \begin{itemize}
      \item one payment 1.75 EUR
      \item one payment 1.91 EUR
    \end{itemize}
      \item Direct donations: 5 EUR 2 times (Antoine Amarilli)
\end{itemize}

Balance: deficit of 960.70 EUR.

The bank account on August 29, 2022 now contains: 830.07 EUR.

We expect to receive payments from ENS of the hosting fees since from August 1, 2021 to July 31, 2022, for a total of 1741.80 EUR ; and then one more payment. This means that, considering only hosting fees, we expect the balance at the end of the project duration (January 31st, 2023) to be 2721.82 EUR; giving us around 1.5 years of funds for hosting.

The project receives 0.51 EUR/week from 2 anonymous donors on Liberapay.

Remark for next invoicing: the hosting fees charged to ENS consider that the cost is 145.15 EUR/month, but it is 149.95 EUR/month since January 2022. In addition to increasing the amount for the fourth invoice, we should add the 33.6 EUR that we did not charge them (4.80 EUR times 7 months).

Le bilan financier est mis aux voix. Il est approuvé à l'unanimité.

\section{Élection du conseil d'administration}

Antoine Amarilli, Antonin Delpeuch et Marie Farge candidatent aux fonctions de
membre du conseil d'administration. Leur candidature est approuvée à
l'unanimité.

Le conseil d'administration nouvellement élu promeut Pierre Senellart au rang de
membre actif, et décide que Patricia Mirabile et Lucas Verney seront membres
associés.

\section{Discussions diverses}

L'assemblée discute d'autres points sur les développments courants de la
plateforme.

L'ordre du jour étant épuisé, la séance est levée à 20h25.

\end{document}
