\documentclass[a4paper]{article}

\usepackage[official]{eurosym}
\usepackage{babel}
\usepackage{hyperref}

\title{Procès-verbal de l'assemblée générale 2023}
\date{19 juillet 2023}

\begin{document}

\maketitle

L'assemblée générale ordinaire du Comité pour l'Accessibilité aux Publications
en Sciences et Humanités (C.A.P.S.H.) s'est tenue le 19 juillet 2023 à 17h05,
sur la plateforme de discussion en ligne BigBlueButton du département INFRES de Télécom Paris.

\begin{itemize}
  \item Présidence de séance : Antoine Amarilli
  \item Secrétaire de séance : Antoine Amarilli
  \item Liste des présents : Antoine Amarilli, Antonin Delpeuch, Marie Farge, N
    Smith
\end{itemize}

\section{Ordre du jour}

\begin{itemize}
\item Bilan moral
\item Bilan financier
\item Élection du conseil d'administration
\item Disccussions diverses
\end{itemize}

\section{Bilan moral}

N Smith présente le bilan moral de l'association (en anglais).

The main effort is to update the Crossref ingestion. The data is now ingested in a secondary table.

The Sherpa/Romeo integration is now complete, but with the existing state of the Dissemin code. There still remains the need to update Dissemin to use all the power of the new schema of Sherpa/Romeo.

The contract of N was originally supposed to end on Feb 2024, and may be extended a bit.

Le bilan moral est mis aux voix et il est approuvé à l'unanimité.

\section{Bilan financier}

Antoine Amarilli présente le bilan financier de l'association (en anglais).

At the latest financial report at the 2022 AGM on August 29, 2022, our bank account contained: 830.07 EUR.

Since then the following happened:

\begin{itemize}
  \item Spendings (total 1715.39 EUR):
\begin{itemize}
  \item Online hosting:
\begin{itemize}
  \item 149.95 EUR 3 times
      \item 172.45 EUR 7 times
\end{itemize}
    \item Gandi : 58.39 EUR via Antoine Amarilli
\end{itemize}

\item Income (total 1760.34 EUR):
  \begin{itemize}
    \item ENS two times 870.90 EUR to pay for 12 months of server hosting : this amount is an underestimate because the Online fees increased, the next invoices will reflect this
    \item 6.70 EUR of "balance discounts" by Wise
    \item 1.88 EUR + 9.96 EUR of Stripe payouts (probably Liberapay), total 11.84 EUR
  \end{itemize}
\end{itemize}

The total is a positive income of 44.95 EUR.

As of June 26, 2023, the bank account contains: 875.02 EUR.

We have received since then an additional payment of 944.70 EUR from ENS to cover the hosting costs, until January 31, 2023. We will later continue to invoice them for one more year.

The project receives 0.51 EUR/week from 2 anonymous donors on Liberapay.

Le bilan financier est mis aux voix. Il est approuvé à l'unanimité.

\section{Élection du conseil d'administration}

Antoine Amarilli, Antonin Delpeuch et Marie Farge candidatent aux fonctions de
membre du conseil d'administration. Leur candidature est approuvée à
l'unanimité.

\section{Discussions diverses}

L'assemblée discute d'autres points sur les développments courants de la
plateforme.

L'ordre du jour étant épuisé, la séance est levée à 17h32

\end{document}
